Milestone 4

### 2021-11-04 perf_release_criteria/milestone_4/ms_4_training_subsetting_calculation.Rmd

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/modeling.R')
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(bigrquery)
library(DBI)
library(lubridate)
library(htmltab)
library(stringr)
```

@@

```{r version, echo=FALSE}
sched <- htmltab('https://wiki.mozilla.org/Release_Management/Calendar', which=2) %>%
  mutate('rel_dates' = ymd(sched$`Release Date`)) %>%
  mutate('version' = as.numeric(str_match(sched$Beta, 'Firefox ([0-9]+)')[,2])) %>%
  filter(rel_dates < now())

@@

df_train <- load_df(paste("ccd_subBeta_training", v_n, sep='_'))
df_predict <- load_df(paste('ccd_subBeta_prerelease'), v_n1, sep='_')
df_validate <- load_df(paste('ccd_subBeta_validation'), v_n, sep='_')
```

@@

df_predict_f <- stage_2_clean(df_predict) %>%
    mutate(date_created = now())
```

@@

Calculate the Release Health Metrics:
**TBD**

@@

```{r serialize_datasets}
# training datasets
# train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
train_file_name <- paste('df_train_', v_n, sep='_')
train_file_path <- file.path('data', train_file_name)
save(df_train_f, df_predict_f, df_train_x, model, file = train_file_path)
gcs_train_file_path <- file.path('data', 'milestone4', train_file_name)

# final prelease subsetted dataset
# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
prerelease_file_name <- paste('df_prerelease_', v_n1, sep='_')
prerelease_file_path <- file.path('data', prerelease_file_name)
save(predictions, file = prerelease_file_path)
gcs_prerelease_file_path <- file.path('data', 'milestone4', prerelease_file_name)

# validation dataset
# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
validation_file_name <- paste('df_validation_', v_n1, sep='_')
validation_file_path <- file.path('data', validation_file_name)
save(validation, file = validation_file_path)
gcs_validation_file_path <- file.path('data', 'milestone4', validation_file_name)

# Release health metrics
release_health_file_name <- paste('df_release_health_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
release_health_file_path <- file.path('data', release_health_file_name)
# save(df_release_health_f, df_predict_f, df_release_health_x, file = release_health_file_path)
gcs_release_health_file_path <- file.path('data', 'milestone4', release_health_file_name)
```

@@

```{r gcp_health_metrics_storage_push, warning=FALSE}
# upload_try <- gcs_upload(gcs_release_health_file_path, name = gcs_file_path)
# upload_try
```

@@

Training and prerelease datasets
```{r big_query_write}
project <- "moz-fx-dev-cdowhyglund-subBeta"
# project <- "moz-fx-data-bq-data-science"

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "training",
         table   = paste("ccd_subbeta_training_cleaned", v_n, sep = '_')) %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_train_x) )

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "training",
         table   = paste("ccd_subbeta_training_final", v_n, sep = '_')) %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_train_x) )

bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "prerelease",
         table   = paste("ccd_subbeta_prelease_cleaned", v_n1, sep = '_')) %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_predict_f) )

@@

Subsetted dataset
```{r bq_write_subset}
bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "prerelease",
         table   = paste("ccd_subbeta_prelease_subset", v_n1, sep = '_')) %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_predict_f) )
```

Validation dataset
```{r bq_write_validate}
bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
         dataset = "validation",
         table   = paste("ccd_subbeta_validation_cleaned", v_n, sep = '_')) %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_predict_f) )
```

Release health Metrics
```{r bq_release_health_metrics}
# bq_table(project = 'moz-fx-dev-cdowhyglund-subbeta',
#          dataset = "prerelease",
#          table   = "ccd_subbeta_prerelease_health_metrics") %>%
#   bq_table_upload(values = release_health_df,
#                   create_disposition = "CREATE_IF_NEEDED",
#                   write_disposition = "WRITE_APPEND",
#                   fields = as_bq_fields(release_health_df) )
```

>>>>

```{r imports, echo=FALSE, warning=FALSE, message=FALSE}
source('../lib/modeling.R')
source('../lib/supporting_funcs.R')
source('../lib/scoring.R')
library(bigrquery)
library(DBI)
library(lubridate)
library(htmltab)
library(stringr)
library(purrr)
```

@@

```{r version, echo=FALSE}
sched <- htmltab('https://wiki.mozilla.org/Release_Management/Calendar', which=2) %>%
  mutate('rel_dates' = ymd(`Release Date`)) %>%
  mutate('version' = as.numeric(str_match(Beta, 'Firefox ([0-9]+)')[,2])) %>%
  filter(rel_dates < now())

@@

df_train <- load_df(paste("ccd_subBeta_training", v_n, sep='_'))
df_predict <- load_df(paste('ccd_subBeta_prerelease', v_n1, sep='_'))
# df_validate <- load_df(paste('ccd_subBeta_validation', v_n, sep='_'))
df_validate <- load_df(paste('ccd_subset_validation', v_n, sep='_'))
```

@@

df_predict_f <- stage_2_clean(df_predict) %>%
    mutate(date_created = now())

df_validate_f <- stage_2_clean(df_validate) %>%
    mutate(date_created = now())
```

@@

Calculate the Release Health Metrics, by comparing the performance metrics of the subsetted Beta dataset to the current validation (version N) Release dataset:

* Beta mean 
* Beta quantiles
* relative difference in mean
* relative difference in deciles
* Cramér-von Mises score

```{r release_health}
agg_sets <- function(predictions){
  predictions %>% 
  select(outcomes) %>% 
  gather("metric", "value", ) %>%
  group_by(metric) %>%
  summarise(
    mean = mean(value),
    p5 = partial(quantile, probs = .05)(value),  
    p25 = partial(quantile, probs = .25)(value),  
    p50 = median(value),
    p75 = partial(quantile, probs = .75)(value),  
    p95 = partial(quantile, probs = .95)(value),
    p99 = partial(quantile, probs = .99)(value)
  )
}

pred_agg <- agg_sets(predictions)
release_agg <-  agg_sets(df_validate_f)

abs_rel_diff <- (abs(pred_agg[-1]-release_agg[-1])/release_agg[-1])
names(abs_rel_diff) <- paste('rel_diff_', names(abs_rel_diff), sep='')
abs_rel_diff <- abs_rel_diff %>%
  mutate(metric = pred_agg$metric)

# cms_score <- calc_score(
#   predictions %>% 
#     select(label, outcomes) %>%
#     bind_rows(
#       select(df_validate_f, label, outcomes)
#   ))

cms_score <- sapply(outcomes, calc_cms, beta=df_predict_f, release=df_validate_f)
cms_score <- data.frame(cms_score) %>% mutate(metric = rownames(.))

health_metrics <- pred_agg %>% 
  inner_join(., abs_rel_diff, by='metric') %>%
  inner_join(., cms_score, by='metric') %>%
  # mutate(cms_score = cms_score) %>%
  mutate(date_created = now()) %>%
  mutate(version = v_n1)
```

@@

```{r serialize_datasets}
# training datasets
# train_file_name <- paste('df_train_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
train_file_name <- paste('df_train_', v_n, '.RData', sep='')
train_file_path <- file.path('data', train_file_name)
save(df_train_f, df_predict_f, df_train_x, model, file = train_file_path)
gcs_train_file_path <- file.path('data', 'milestone4', train_file_name)

# final prelease subsetted dataset
# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
prerelease_file_name <- paste('df_prerelease_', v_n1, '.RData', sep='')
prerelease_file_path <- file.path('data', prerelease_file_name)
save(predictions, file = prerelease_file_path)
gcs_prerelease_file_path <- file.path('data', 'milestone4', prerelease_file_name)

# validation dataset
# prerelease_file_name <- paste('df_prerelease_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
validation_file_name <- paste('df_validation_', v_n1, '.RData', sep='')
validation_file_path <- file.path('data', validation_file_name)
save(df_validate_f, file = validation_file_path)
gcs_validation_file_path <- file.path('data', 'milestone4', validation_file_name)

# Release health metrics
# release_health_file_name <- paste('df_release_health_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
release_health_file_name <- paste('df_release_health_', v_n1, '_', format(Sys.time(), "%Y%m%d"), '.RData', sep='')
release_health_file_path <- file.path('data', release_health_file_name)
save(health_metrics, file = release_health_file_path)
gcs_release_health_file_path <- file.path('data', 'milestone4', release_health_file_name)
```

@@

```{r gcp_health_metrics_storage_push, warning=FALSE}
upload_try <- gcs_upload(release_health_file_path, name = gcs_release_health_file_path)
upload_try
```

@@

Training and prerelease datasets
```{r big_query_write}
project <- "moz-fx-dev-cdowhyglund-subbeta"
# project <- "moz-fx-data-bq-data-science"

bq_table(project = project,
         dataset = "training",
         table   = paste("ccd_subbeta_training_cleaned", v_n, sep = '_')) %>%
  bq_table_upload(values = df_train_x,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_train_x) )

bq_table(project = project,
         dataset = "training",
         table   = paste("ccd_subbeta_training_final", v_n, sep = '_')) %>%
  bq_table_upload(values = df_train_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_train_f) )

bq_table(project = project,
         dataset = "prerelease",
         table   = paste("ccd_subbeta_prelease_cleaned", v_n1, sep = '_')) %>%
  bq_table_upload(values = df_predict_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(df_predict_f) )

@@

Subsetted dataset
```{r bq_write_subset}
bq_table(project = project,
         dataset = "prerelease",
         table   = paste("ccd_subbeta_prelease_subset", v_n1, sep = '_')) %>%
  bq_table_upload(values = predictions,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_TRUNCATE",
                  fields = as_bq_fields(predictions) )
```

Validation dataset
```{r bq_write_validate}
bq_table(project = project,
         dataset = "validation",
         table   = paste("ccd_subbeta_validation_cleaned", v_n, sep = '_')) %>%
  bq_table_upload(values = df_validate_f,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(df_validate_f) )
```

Release health Metrics
```{r bq_release_health_metrics}
bq_table(project = project,
         dataset = "prerelease",
         table   = "ccd_subbeta_prerelease_health_metrics") %>%
  bq_table_upload(values = health_metrics,
                  create_disposition = "CREATE_IF_NEEDED",
                  write_disposition = "WRITE_APPEND",
                  fields = as_bq_fields(health_metrics) )
```
